Comprehensive quality - aware Automated Semantic Web Service Composition

### 2016-11-03 paper.tex
update

In this section, we analyse the composition solution generated by using our approach. In particularly, we show that our proposed approach can produce solutions that results better matchmaking , which meets user's goal better.
Now we look at $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$ defined in the solution model using black-box testing for the comparison, where the comprehensive quality awareness approach and QoS awareness approach \cite{feng2013dynamic,huang2009effective,ma2015hybrid,da2014graph} are compared to reveal how good our evaluation mode is in a decision table shown in Table \ref{decisionTable}. Solutions to five tasks are compared using two evaluation models in WSC09. In each task, we compare $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$, and $Q_{QoS}$ is normalised to make it comparable to another method in our comprehensive awareness approach

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table}[]
\footnotesize
\centering
\caption{Quality of two evaluation model in a decision table}
\label{decisionTable}
\begin{tabular}{|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{\multirow{2}{*}{}}                              &Approach 1           &Approach 2                           \\ \cline{3-4} 
\multicolumn{2}{|c|}{}                                               & \shortstack{QoS-aware \\ Evaluation} & \shortstack{Comprehensive \\ Quality Evaluation} \\ \hline
\multirow{3}{*}{Condition}            & dataset1             & $\surd$              & $\surd$                            \\ \cline{2-4} 
                                      & dataset2             & $\surd$              & $\surd$                            \\ \cline{2-4} 
                                      & dataset3             & $\surd$              & $\surd$                            \\ \hline
\multirow{3}{*}{\shortstack{Task1\\Optimised solution}}  &$Q_{mt}$   & .232635              & .232635                          \\ \cline{2-4} 
                                      &$Q_{s}$                       & .903572              & .903572                          \\ \cline{2-4}
                                      &$Q_{QoS}$                     & .578577              & .578577                          \\ \hline
\multirow{3}{*}{\shortstack{Task2\\Optimised solution}}  &$Q_{mt}$   & .001828              & .000851$\downarrow$               \\ \cline{2-4} 
                                      &$Q_{s}$                       & .917172              & .938840$\uparrow$                 \\ \cline{2-4}
                                      &$Q_{QoS}$                     & .480251              & .473002$\downarrow$               \\ \hline
\multirow{3}{*}{\shortstack{Task3\\Optimised solution}}  &$Q_{mt}$   & .191188              & .247836$\uparrow$                  \\ \cline{2-4} 
                                      &$Q_{s}$                       & .951509              & .973723$\uparrow$                  \\ \cline{2-4}
                                      &$Q_{QoS}$                     & .493927              & .491538$\downarrow$                 \\ \hline
\multirow{3}{*}{\shortstack{Task4\\Optimised solution}}  &$Q_{mt}$   & .919678              & .943406$\uparrow$                  \\ \cline{2-4} 
                                      &$Q_{s}$                       & .000000              & .000009$\uparrow$                  \\ \cline{2-4}
                                      &$Q_{QoS}$                     & .480818              & .472485$\downarrow$                 \\ \hline
\multirow{3}{*}{\shortstack{Task5\\Optimised solution}}  &$Q_{mt}$   & .000094              & .000109$\uparrow$                  \\ \cline{2-4} 
                                      &$Q_{s}$                       & .927476              & .930975$\uparrow$                  \\ \cline{2-4}
                                      &$Q_{QoS}$                     & .476236              & .475128$\downarrow$                 \\ \hline                                                   
\end{tabular}
\end{table}
In Table \ref{decisionTable}, Task 1 represents the same solution using different methods where the values of $Q_{mt}$,$Q_{s}$ and $Q_{QoS}$ are all the same. It is due to the size of dataset 01 is very small in both available services and ontologies. However, As the size of dataset increase, we can recognise a trade-offs in task 2 using our evaluation approach, where a 0.021668 increase in similarity quality and a 0.00098 decrease in matchType quality with weights 0.4 and 0.1 respectively so that solution to task 2 is still considered to be an improvement in the functional quality part while a decrease value of 0.007249 in QoS. In task 3, the benefit of functional part quality is clearer with an increase value of 0.056648 and 0.078862 in  similarity quality and matchType quality respectively while a slight decrease in QoS. later on, the rest tasks perform the same behaviour in $Q_{mt}$,$Q_{s}$ and $Q_{QoS}$ as task 3. In conclusion, we can perceive that our evaluation could find out better functional quality with a reasonable trade off in QoS.

@@

@@

Firstly, the average fitness value with optimum is calculated by the average value of best fitness found in each generation over 30 independent runs. The value plotted in the first column group ranges from 0 to 1 in figure \ref{exp_fitnessvalue}, and it is considered to be more optimised if its value is closer to value 1. We can see that there is a significant increase in the fitness value (avg) with optimum between generation 0 and generation 15-25, the remained generation continues to produce a steady but moderate improvement in the fitness value and eventually reach a plateau with no further changes. The same behaviour is observed over the rest tasks. Also, there is a fast convergence of the fitness value that be observed. That is simply because of many repetitive solutions in the indirect web service composition representations in the search space.

We also investigate the variation of two factors consisted in the functional quality part --- average matchType quality with optimum and average similarity quality with optimum from generation 0 to 99 in second and third column groups of Figure \ref{exp_fitnessvalue}. In these groups,  both the average matchType quality with optimum and average similarity quality with optimum are the mean value corresponding to the best fitness value found in each generation over 30 independent runs. The dominant tendency of the marked value representing a similar characteristic compared to the average fitness value group trend in five tasks. However, there are some slight fluctuations over the generations, it due to the single objective fitness function that prevents selecting the worst component quality without granting for the best.

Lastly, It is interesting to look at the average QoS per generation for the 30 independent runs when the behaviour of functional quality moves upward. Here average QoS with optimum is also the value corresponding to the fitness value with optimum in each generation, and we display the results in the fourth column group in Figure \ref{exp_fitnessvalue}. It is obvious that the overall trend of QoS moves upward to a high constant level in five independent tasks. Additionally, we don't see too much trade-off from the QoS.

\section{Conclusion}\label{conclusion}
This work introduced a more applicable and simpler evaluation model for comprehensive quality awareness semantic automated web service composition that relies on semantic matchmaking quality extension to QoS-aware consideration. The key idea of these evaluation model is to consider the quality of semantic matchmaking corresponding to different matchmaking types. Also, the effectiveness of our model is also proved to obtain better functional quality with a reasonable trade-off in QoS. Future works in this area should investigate more reasonable matching types, explore the comprehensive quality in multi-objective approach, and improve efficiency in the functional quality calculation.
\bibliographystyle{splncs03}
\bibliography{bibliography}

>>>>

In this section, we analyse the composition solution generated by using our approach comparing with QoS-aware approach. In particularly, we show that our proposed approach can produce solutions that results better matchmaking , which meets user's goal better. In particularly, we look at mean value of $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$ in the comprehensive quality awareness approach and QoS awareness approach are compared to reveal how good our evaluation mode in Table \ref{decisionTable}. In each task, we compare $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$, and $Q_{QoS}$ is normalised to make it comparable to another method in our comprehensive awareness approach

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table}[]
\footnotesize
\centering
\caption{Mean Quality for comprehensive quality-aware methods and QoS-aware appraoch}
\label{decisionTable}
\begin{tabular}{|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{}                                               & \shortstack{QoS-aware \\ Evaluation} & \shortstack{Comprehensive \\ Quality Evaluation} \\ \hline
\multirow{3}{*}{Task1}  &$Q_{mt}$   & .232635              & .232635                          \\ \cline{2-4} 
                                      &$Q_{s}$                       & .903572              & .903572                          \\ \cline{2-4}
                                      &$Q_{QoS}$                     & .578577              & .578577                          \\ \hline
\multirow{3}{*}{Task2}  &$Q_{mt}$   & .001828              & .000851$\downarrow$               \\ \cline{2-4} 
                                      &$Q_{s}$                       & .917172              & .938840$\uparrow$                 \\ \cline{2-4}
                                      &$Q_{QoS}$                     & .480251              & .473002$\downarrow$               \\ \hline
\multirow{3}{*}{Task3}  &$Q_{mt}$   & .191188              & .247836$\uparrow$                  \\ \cline{2-4} 
                                      &$Q_{s}$                       & .951509              & .973723$\uparrow$                  \\ \cline{2-4}
                                      &$Q_{QoS}$                     & .493927              & .491538$\downarrow$                 \\ \hline
\multirow{3}{*}{Task4}  &$Q_{mt}$   & .919678              & .943406$\uparrow$                  \\ \cline{2-4} 
                                      &$Q_{s}$                       & .000000              & .000009$\uparrow$                  \\ \cline{2-4}
                                      &$Q_{QoS}$                     & .480818              & .472485$\downarrow$                 \\ \hline
\multirow{3}{*}{Task5}  &$Q_{mt}$   & .000094              & .000109$\uparrow$                  \\ \cline{2-4} 
                                      &$Q_{s}$                       & .927476              & .930975$\uparrow$                  \\ \cline{2-4}
                                      &$Q_{QoS}$                     & .476236              & .475128$\downarrow$                 \\ \hline                                                   
\end{tabular}
\end{table}
In Table \ref{decisionTable}, Task 1 represents the same solution using different methods where the values of $Q_{mt}$,$Q_{s}$ and $Q_{QoS}$ are all the same. It is due to the size of dataset 01 is very small in both available services and ontologies. However, As the size of dataset increase, we can recognise a trade-offs in task 2 using our evaluation approach, where a 0.021668 increase in similarity quality and a 0.00098 decrease in matchType quality with weights 0.4 and 0.1 respectively so that solution to task 2 is still considered to be an improvement in the functional quality part while a decrease value of 0.007249 in QoS. In task 3, the benefit of functional part quality is clearer with an increase value of 0.056648 and 0.078862 in  similarity quality and matchType quality respectively while a slight decrease in QoS. later on, the rest tasks perform the same behaviour in $Q_{mt}$,$Q_{s}$ and $Q_{QoS}$ as task 3. In conclusion, we can perceive that our evaluation could find out better functional quality with a reasonable trade off in QoS.

@@

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table}[]
\centering
\caption{My caption}
\label{my-label}
\begin{tabular}{|l|l|l|l|l|}
\hline
\multicolumn{2}{|l|}{} & Comprehensive-aware & QoS-aware &  $\Delta Q$\\ \hline
\multirow{2}{*}{e1} &$q(e_{mt})$        &        1   &  1 &0\\ \cline{2-5} 
                    & $q(e_{s})$                    &     1      & 1& 0\\ \hline
\multirow{2}{*}{e2} & $q(e_{mt})$                     &    0.9167       & 0.75 & \\ \cline{2-5} 
                    &   $q(e_{s})$                    &   0.9630        & 0.9232 &\\ \hline
\multirow{2}{*}{e3} &  $q(e_{mt})$                   &    0.8333       & 0.75 &\\ \cline{2-5} 
                    &   $q(e_{s})$                    &    0.9608       &  0.8230 &\\ \hline
\multirow{2}{*}{e4} & $q(e_{mt})$                      &    0.875       & 0.75 &\\ \cline{2-5} 
                    &  $q(e_{s})$                     &    0.9167       & 0.9090 &\\ \hline
\multicolumn{2}{|l|}{SM} &                     &           &  \\ \hline
\multicolumn{2}{|l|}{QoS} &        0.4915             &  0.4949         &  \\ \hline
\end{tabular}
\end{table}

@@

Firstly, the average fitness value with optimum is calculated by the average value of best fitness found in each generation over 30 independent runs. The value plotted in the first column group ranges from 0 to 1 in figure \ref{exp_fitnessvalue}, and it is considered to be more optimised if its value is closer to value 1. We can see that there is a significant increase in the fitness values with optimum between generation 0 and generation 15-25, the remained generation continues to produce a steady but moderate improvement in the fitness value and eventually reach a plateau with no further changes. The same behaviour is observed over the rest tasks. Also, there is a fast convergence of the fitness value that be observed. That is simply because of many repetitive solutions in the indirect web service composition representations in the search space.

We also investigate the variation of two factors consisted in the functional quality part --- average matchType quality with optimum and average similarity quality with optimum from generation 0 to 99 in second and third column groups of Figure \ref{exp_fitnessvalue}. In these groups,  both the average matchType quality with optimum and average similarity quality with optimum are the mean value corresponding to the best fitness value found in each generation over 30 independent runs. The dominant tendency of the marked value representing a similar characteristic compared to the average fitness value group trend in five tasks. However, there are some slight fluctuations over the generations, due to the single objective fitness function that prevents selecting the worst component quality without granting for the best.

Lastly, it is interesting to look at the average QoS per generation for the 30 independent runs when the behaviour of functional quality moves upward. Here average QoS with optimum is also the value corresponding to the fitness value with optimum in each generation, and we display the results in the fourth column group in Figure \ref{exp_fitnessvalue}. It is obvious that the overall trend of QoS moves upward to a high constant level in five independent tasks. Additionally, we don't see too much trade-off from the QoS.

\section{Conclusion}\label{conclusion}
This work introduced a evaluation model for QoS-aware automated semantic automated web service composition that is based on a semantic matchmaking quality extends existing QoS. The results shows that our comprehensive quality model is proved to obtain better functional quality with a reasonable trade-off in QoS. Future works in this area could explore the comprehensive quality with multi-objectives to maximising quality of matchmaking and to optimise QoS, and improve efficiency in calculating semantic quality.
\bibliographystyle{splncs03}
\bibliography{bibliography}
